Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-06 tex/VHzQ.tex
tex/VHzQ.* update

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. The near-infrared data comes from
two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

@@

For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.  For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.

@@

Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table. However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection informationn.

@@

Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band. In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude. The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4. With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detectiopns in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
%%AllWISE Source Catalog

@@

Recently, \citet{Assef2018} released two large catalogues of AGN 
candidates identified across 30,000 deg$^2$ of extragalactic sky 
from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
AGN candidates per deg$^2$) while the ``C75'' catalogue  
consists of 20.9M AGN candidates at 75\% completeness (and 
($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
out catalogue of 463 VH$z$Qs with these catalogues, produces 
42 matches with	the R90 sample and 98 matches with the C75 sample. 
Both catalogues unsurprisingly match to the ultraluminous quasar 
SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
matches J1342+0928 \citep{Banados2018}.

@@

Thenn a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependenet o nthe averaging timescales (whcih as we see can vary).

@@

Longer time-series, better SNR and moreover, $(1+z)$. 
Just selecting things that would
%%
Doing this independtly in each band...
%Variation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surface Density of VH$z$Qs}
One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
so, how many are still to be discovered and confirmed spectroscopcially?

VHS, Area 1: 150$<$RA/deg$<200$ annd $-40<$Decl./deg$<-20$:
$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, ompiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

@@

\subsection*{Author Contributions}   
N.P.R. initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
%%
N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
%%

>>>>

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. The near-infrared data comes from
two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarily, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

@@

For the two shorter WISE bands, $\lambda_{\rm eff}$3.37$\mu$m W1 and $\lambda_{\rm eff}$4.62$\mu$m W2 we generally report the deeper, unblurred unWISE coadd data.  For the two longer WISE bands, $\lambda_{\rm eff}$12.1$\mu$m and $\lambda_{\rm eff}$22.8$\mu$m we use the ALLWISE Data Release.  Most objects in the AllWISE Source Catalog are unresolved, so the best photometric measurements to use are the deep detection profile-fit photometry measures,  {\tt w$x$mpro},  {\tt w$x$sigmpro} and  {\tt w$x$snr}. The unWISE Catalog absolute photometric calibration derives from the photometric calibration of the unWISE coadds \citep{Meisner2017a}, which is tied to the original WISE zero points through aperture fluxes in a 27.5'' radius.

@@

Knowing we have secure detections in the near-infrared bands, and wanting to boost the number of WISE W3/W4 detections, we allow ourselves to be less conservative in querying the ALLWISE catalogues and also query the AllWISE Reject Table. However, with the exception of one object (SHELLQs  J1208-0200), the ALLWISE Reject Table does not contain any further W3/W4 detection information.

@@

Before reporting on the detection rates, we investigate this effect using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage} shows the WISE ALLWISE magnitude versus signal-to-noise, colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band. In the two shorter bands W1/2 we see the clear and expected trend for brighter objects to have larger SNR, and also for the higher signal to noise for objects with more exposures at a given magnitude. The behaviour for the W3/4 bands is different, with two populations clearly evident in W3 and although a bit more mixed, also in W4. With the suggested split at SNR$>2$, and no obvious R.A./Declination dependence seen, this behaviour is explained by the fact that there are non-detections in W3/4 for objects (with high W1/2 SNR) that are reported in the ALLWISE catalogue.
%%AllWISE Source Catalog

@@

Recently, \citet{Assef2018} released two large catalogues of AGN 
candidates identified across 30,000 deg$^2$ of extragalactic sky 
from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
AGN candidates per deg$^2$) while the ``C75'' catalogue  
consists of 20.9M AGN candidates at 75\% completeness (and 
($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
out catalogue of 463 VH$z$Qs with these catalogues, produces 
42 matches with	the R90 sample and 98 matches with the C75 sample. 
Both catalogues unsurprisingly match to the ultraluminous quasar 
SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
matches J1342+0928 \citep{Banados2018}.

@@

Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).

@@

Longer time-series, better SNR and moreover, $(1+z)$. 
Just selecting things that would
%%
Doing this independently in each band...
%Variation

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surface Density of VH$z$Qs}
One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
so, how many are still to be discovered and confirmed spectroscopically?

VHS, Area 1: 150$<$RA/deg$<200$ and $-40<$Decl./deg$<-20$:
$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%  S E C T I O  N   7         S E C T I O  N   7           S E C T I O  N   7       S E C T I O  N   7
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and Conclusions}
\label{sec:conclusions}
In this study, we have, for the first time, compiled the list of all
$z>5$ spectroscopically confirmed quasars. We have assemble the NIR
($y/Y, J, H, K/K_{s}$) and MIR (WISE W1/2/3/4) photometry for these
objects, given their detection rates and SEDs. We find that:

@@

\subsection*{Author Contributions}   
N.P.R. initiated the project, compiled the list of $z>5.00$ quasars, wrote most of the analysis code, developed the the plotting scripts, and developed and wrote the initial and subsequent drafts of the manuscript.
%%
N.J.G.C. supplied the critical near-infrared expertise and database for which the bulk of the project relies. N.J.G.C. also contributed directly to the writing of the manuscript.
